What makes musicians infer teaching intentions?

### 2023-01-17 paper/manuscript.Rmd
correct typo
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Apparatus
The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; https://www.psychopy.org/) on a Mac Book Pro with Mac OS X Catalina 10.15.6. Stimuli were played using the Mido Python library (1.2.9; https://mido.readthedocs.io/en/latest/) on a Max/MSP patcher (8.1.7; https://cycling74.com/products/max). During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).

>>>>

## Apparatus
The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; https://www.psychopy.org/) on a MacBook Pro with Mac OS X Catalina 10.15.6. Stimuli were played using the Mido Python library (1.2.9; https://mido.readthedocs.io/en/latest/) on a Max/MSP patcher (8.1.7; https://cycling74.com/products/max). During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).

### 2023-01-17 paper/manuscript.tex
correct typo
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; \url{https://www.psychopy.org/}) on a Mac Book Pro with Mac OS X Catalina 10.15.6. Stimuli were played using the Mido Python library (1.2.9; \url{https://mido.readthedocs.io/en/latest/}) on a Max/MSP patcher (8.1.7; \url{https://cycling74.com/products/max}). During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).

>>>>

The experiment was programmed in Python 3.8.2 using the PsychoPy Python library (2020.2.4; \url{https://www.psychopy.org/}) on a MacBook Pro with Mac OS X Catalina 10.15.6. Stimuli were played using the Mido Python library (1.2.9; \url{https://mido.readthedocs.io/en/latest/}) on a Max/MSP patcher (8.1.7; \url{https://cycling74.com/products/max}). During the experiment, participants listened to the stimuli via headphones (Audio-Technica ATH-M50X).
